---
title: "RWorksheet_Aguas4"
author: "Diana Marie Aguas"
date: "2022-11-25"
output: pdf_document
---

1. The table below shows the data about shoe size and height. Create a data frame.
```{r, error=TRUE}
Shoe_size <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,10.5)
Shoe_size

Height <- c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,71.0)
Height

Gender <- c("F","F","F","F","M","F","F","F","M","F","M","F","M","M")
Gender

Shoesize <- c(13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)
Shoesize

Height_ <- c(77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,69.0,72.0,70.0,69.0,70.0)
Height_

Gender_ <- c("M","M","F","F","M","F","F","M","M","F","M","M","M","M")
Gender_

df <- data.frame(Shoe_size, Height, Gender, Shoesize, Height_, Gender_)
```
a. Describe the data
-It shows the differences between women and mens shoe size and height.
b.
```{r, error=TRUE}
mean_1 <- mean(Shoe_size)
mean_1

mean_2 <- mean(Shoesize)
mean_2

res <- c(mean_1, mean_2)
res

meanshoes <- mean(res)
meanshoes

mean_3 <- mean(Height)
mean_3

mean_4 <- mean(Height_)
mean_4

res2 <- c(mean_3, mean_4)
res2

meanheight <- mean(res2)
meanheight
```
c.
```{r, error=TRUE}
meanhsh <- mean(c(meanshoes, meanheight))
meanhsh
```
-There is a relationship between the height and shoe size because when the person is short,
then the shoe size is small and when the person is tall, then the shoe size is big.

#FACTORS

2. Construct character vector months to a factor with factor() and assign the result to
factor_months_vector. Print out factor_months_vector and assert that R prints out
the factor levels below the actual values.
```{r, error=TRUE}
months_vector <- c("March", "April", "January", "November", "January", "September","October", "September", "November", "August", "January", "November","November", "February", "May", "August", "July", "December", "August","August", "September", "November", "February", "April")

factor_months_vector <- factor(months_vector)
factor_months_vector
```
3. Then check the summary() of the months_vector and factor_months_vector. 
Interpret the results of both vectors. Are they both equally useful in this case?
```{r, error=TRUE}
months_summ <- summary(months_vector)
months_summ

months_summ2 <- summary(factor_months_vector)
months_summ2
```
4. Create a vector and factor for the table below.
```{r, error=TRUE}
factor_data <- c("East" = '1', "West" = '4', "North" = '3')
factor_data

new_order_data <- factor(factor_data, levels = c("East" = '1', "West" = '4', "North" = '3'))
print(new_order_data)
```
5. Enter the data below in Excel with file name = import_march.csv
a.
```{r,error=TRUE}
import <- read.table("/cloud/project/RWorksheet3,4,5/import_march.csv",header = TRUE, sep = ",")
import
```
b.
```{r,error=TRUE}
view <- read.csv("/cloud/project/RWorksheet3,4,5/import_march.csv")
view
```
