---
title: "RWorksheet_Aguas#6"
author: "Diana Marie Aguas"
date: "2022-11-30"
output: pdf_document
---

```{r, include=TRUE}
library(dplyr)
library(ggplot2)

data(mpg)
dataA <- as.data.frame(mpg)
```
1. How many columns are in mpg dataset? How about the number of rows? Show the
codes and its result. #Ans: The mpg dataset has 234 rows and 11 colums.
```{r, include=TRUE}
rowncol <- c(nrow(mpg), ncol(mpg))
rowncol
```
2. Which manufacturer has the most models in this data set? Which model has the most
variations? Ans: The manufacturer that has the most model in this data set is dodge
with the model caravan 2wd
```{r, include= TRUE}
carvar <- dataA %>% group_by(manufacturer, model) %>%
  count()
carvar

colnames(carvar) <- c("Manufacturer", "Model", "Counts")
```
a. Group the manufacturers and find the unique models. Copy the codes and result.
```{r, include= TRUE}
uniquemodels <- dataA %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
uniquemodels

colnames(uniquemodels) <- c("Manufacturers", "Model", "Counts")
```
b. Graph the result by using plot() and ggplot(). Write the codes and its result.
```{r, include=TRUE}
plot(carvar)

ggplot(carvar, aes(Model, Manufacturer)) + geom_point()
```
3. Same data set will be used. You are going to show the relationship of the 
model and the manufacturer.
```{r, include=TRUE}
modnmanuf <- mpg

modelfact <- modnmanuf %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
modelfact

colnames(modelfact) <- c("Manufacturer", "Model")
modelfact
```
a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?
```{r, include=TRUE}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```
b. For you, is it useful? If not, how could you modify the data to make it more informative?

### - it is useful, yes, but using legend would be very much useful to summarize the data.

4. Using the pipe (%>%), group the model and get the number of cars per model. 
Show codes and its result.
```{r, include=TRUE}
group_mod <- dataA %>% group_by(model) %>% count()
group_mod

colnames(group_mod) <- c("Model", "Counts")
group_mod
```

a. Plot using the geom_bar() + coord_flip() just like what is shown below. 
Show codes and its result.
```{r, include=TRUE}
qplot(model,data = mpg,main = "Number of Cars per Model", ylab = "Number of Cars",
      xlab = "Model", geom = "bar", fill = manufacturer) +
  coord_flip()
```

b. Use only the top 20 observations. Show code and results.
```{r, include=TRUE}
twenty <- group_mod[1:20,] %>% top_n(2)
twenty

ggplot(twenty, aes(x = Model, y = Counts)) + 
  geom_bar(stat = "identity") + coord_flip()
```

5. Plot the relationship between cyl - number of cylinders and displ - 
engine displacement using geom_point with aesthetic colour = engine 
displacement. Title should be “Relationship between No. of Cylinders and Engine Displacement”.

a. Show the codes and its result.
```{r, include=TRUE}
ggplot(data = mpg , mapping = aes(x = displ, y = cyl, main = "Relationship 
                                    between No of Cylinders and 
                                    Engine Displacement")) + 
  geom_point(mapping=aes(colour = "engine displacement"))
```
b. How would you describe its relationship?

### - cyl is the y in the chart which stands for the number of cylinders
### and displ is the x/engine displacement.

6. Get the total number of observations for drv - type of drive train (f = front-wheel drive,
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.).
Plot using the geom_tile() where the number of observations for class be used as a
fill for aesthetics.

a. Show the codes and its result for the narrative in #6.
```{r, include=TRUE}
ggplot(data = mpg, mapping = aes(x = drv, y = class)) + geom_tile(aes(fill=class))
```

b. Interpret the result.

### - geom_tile() with fill makes it easier to navigate through the chart and identify class(y axis)
### and drive trains(drv- x axis)

7. Discuss the difference between these codes. Its outputs for each are shown below.

# • Code #1
```{r, include=TRUE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

# •Code #2
```{r, include=TRUE}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```
8. Try to run the command ?mpg. What is the result of this command?
```{r, include=TRUE}
?mpg
```
### - It showed the dataset that cointains a subset of the fuel economy data from 
### 1999 to 2008 for 38 popular model cars.

a. Which variables from mpg dataset are categorical?

### -  Manufacturer trans ,model, drv, fl, and class

b. Which are continuous variables?

### - displ, cyl, and hwy

c. Plot the relationship between displ (engine displacement) and hwy(highway miles
per gallon). Mapped it with a continuous variable you have identified in #5-b. What is its
result? Why it produced such output? 
```{r, include=TRUE}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()
```

9. Plot the relationship between displ (engine displacement) and hwy(highway miles
per gallon) using geom_point(). Add a trend line over the existing plot using
geom_smooth() with se = FALSE. Default method is “loess”.
```{r,include=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
```

10. Using the relationship of displ and hwy, add a trend line over existing plot. 
Set these = FALSE to remove the confidence interval and method = lm to 
check for linear modeling.
```{r, include=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) + geom_point() +
  geom_smooth(se = FALSE, method = lm)
```

